---
output:
  github_document:
    toc: yes
    toc_depth: 2
  fig_caption: no
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/lbusett/sprawl.svg?branch=master)](https://travis-ci.org/lbusett/sprawl)
[![codecov](https://codecov.io/gh/lbusett/sprawl/branch/master/graph/badge.svg?token=0yWdr6gWG7)](https://codecov.io/gh/lbusett/sprawl)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)

# sprawl: Spatial Processing (in) R: Amorphous Wrapper Library

Support for spatial processing tasks is provided in `R` by several great packages, spanning 
from all-purpose packages providing generalized access to the main spatial data classes and
corresponding processing methods (e.g.,  [`sp`](https://CRAN.R-project.org/package=sp) and [`sf`](https://CRAN.R-project.org/package=sf), [`raster`](https://CRAN.R-project.org/package=raster) and [`rgdal`](https://CRAN.R-project.org/package=rgdal) - providing functions 
for handling raster and vector spatial data -), to more "specialized" ones meant to allow 
conducting more specific processing tasks (e.g., [`geosphere`](https://CRAN.R-project.org/package=geosphere), [`landsat`](https://CRAN.R-project.org/package=landsat), [`MODIStsp`](https://CRAN.R-project.org/package=MODIStsp)), or to provide 
optimized/improved/easier solutions for methods already provided by the aforementioned
general-purpose packages (e.g., [`velox`](https://CRAN.R-project.org/package=velox), [`mapview`](https://CRAN.R-project.org/package=mapview)) (Curated lists of 
some very good packages can be found [here](https://CRAN.R-project.org/view=Spatial), 
[here](https://ropensci.org/blog/blog/2016/11/22/geospatial-suite) and 
[here](https://github.com/ropensci/maptools)). 

This huge variability provides advanced `R` programmers with great flexibility for conducting 
simple or complex spatial data analyses, by combining functionalities of different packages within
custom scripts. At the same time, it may be confusing for less skilled programmers, who may struggle
with dealing with multiple packages and don't know that a certain processing task may be more
efficiently conducted by using less-known (and sometimes difficult to find) packages. 

**`sprawl`** aims to simplify the execution of some spatial processing tasks by **providing a 
single and (hopefully) simpler access point to functionalities spread in the `R` packages ecosystem, 
introducing optimixed functions for executing frequently used processing tasks, and providing 
custom functions or workflows for the execution of more complex processing tasks** (See [here](https://lbusett.github.io/sprawl/articles/sprawl.html) for further details). 

## **WORK IN PROGRESS !**

If you stumble on this page, please be advised that **`sprawl` is currently in an early stage 
of development. This means that things are going to change rapidly, and we do not guarantee 
that everything works as expected**. Additionally, be warned that until a first official version 
is released, __functions may change behaviour or even completely disappear while we test different 
approaches and solutions!__ (besides this: we would be happy to have beta-testers !)

## Installation

You can install sprawl from git-hub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("lbusett/sprawl")
```

Before installing, __please ensure that GDAL is installed on your machine, and that 
it is on your PATH__.

You can find instructions for installing GDAL 
[HERE](http://lbusett.github.io/MODIStsp/articles/installation.html#installing-gdal-1-11-1)


<font size="2"> _Note that, given its rather broad scope, `sprawl` **imports functions from
several other packages**. Since some of those have quite specific System Requirements, it's 
possible that you'll struggle a bit in installation due to unresolved dependencies. In that 
case, please have a look at the installation error messages to see which package has problems 
in installation and try to install it beforehand (consulting its specific CRAN pages or doing 
a stackoverflow search may help !)._ </font>

## Function Documentation

The main functions available in `sprawl` are documented 
[here](https://lbusett.github.io/sprawl/reference/index.html), along with usage
examples. 

## Examples of use

Worked-out examples of the more comlex `sprawl` functions and workflows can be found [here](https://lbusett.github.io/sprawl/docs/articles/examples.html)

## Contributing

We are open for contributions/help in improving `sprawl` and extend its functionalities. 
If you have a **suggestion for and additional functionality** please report it in our [issues](https://github.com/lbusett/sprawl/issues) page. 
If you **wish to contribute to `sprawl` development**, please see our [Contributing page](articles/articles/contributing.html) 
on Git Hub (COMING SOON !).

## Authors

`sprawl` is currently developed and maintained by Lorenzo Busetto and Luigi Ranghetti of 
CNR-IREA (Institute on Remote Sensing of Environment - National Research Council, Italy - 
http://www.irea.cnr.it/en/)

## Citation

To cite package `sprawl` in publications use:

  Lorenzo Busetto and Luigi Ranghetti (2017). sprawl: Spatial Processing (in) R: Advanced
  Workflow Library. R package version 0.1.0.9000.

Please note that this project is released with a [Contributor Code of Conduct](articles/articles/conduct.html).
By participating in this project you agree to abide by its terms.
