---
output:
  github_document:
    toc: yes
    toc_depth: 2
  fig_caption: no
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/lbusett/sprawl.svg?branch=master)](https://travis-ci.org/lbusett/sprawl)
[![codecov](https://codecov.io/gh/lbusett/sprawl/branch/master/graph/badge.svg?token=0yWdr6gWG7)](https://codecov.io/gh/lbusett/sprawl)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)


# sprawl - Spatial Processing (in) R: Advanced Workflow Library

## Intro and rationale 

Support for spatial processing tasks is provided in `R` by several great packages, spanning from all-purpose packages providing generalized access to the main spatial data classes and corresponding processing methods (e.g.,  [`sp`](https://cran.r-project.org/web/packages/sp/index.html) and [`sf`](https://cran.r-project.org/web/packages/sf/index.html), [`raster`](https://cran.r-project.org/web/packages/raster/index.html) and [`rgdal`](https://cran.r-project.org/web/packages/rgdal/index.html) - providing functions for handling raster and vector spatial data -), to more "specialized" ones meant to allow conducting more specific processing tasks (e.g., [`geosphere`](https://cran.r-project.org/web/packages/geosphere/index.html), [`raster`](https://cran.r-project.org/web/packages/raster/index.html),  [`landsat`](https://cran.r-project.org/web/packages/landsat/index.html), [`MODIStsp`](https://cran.r-project.org/web/packages/MODIStsp/index.html)), or to provide optimized/improved/easier solutions for methods already provided by the aforementioned general-purpose packages (e.g., [`velox`](https://cran.r-project.org/web/packages/velox/index.html), [`mapview`](https://cran.r-project.org/web/packages/mapview/index.html)) (Curated lists of some very good packages can be found [here](https://cran.r-project.org/web/views/Spatial.html), [here]( https://ropensci.org/blog/blog/2016/11/22/geospatial-suite) and [here](https://github.com/ropensci/maptools)). 

This huge variability provides advanced `R` programmers with great flexibility for conducting simple or complex spatial data analyses, by combining functionalities of different packages within custom scripts. At the same time, it may be confusing for less skilled programmers, who may struggle with dealing with multiple packages and don't know that a certain processing task may be more efficiently conducted by using less-known (and sometimes difficult to find) packages. 

In this context, **`sprawl` aims to simplify the execution of some "common" spatial processing tasks** (e.g., reading/writing spatial datasets, extracting statistics from large datasets, etc.) **by providing a single and (hopefully) simpler access point to functionalities spread in the `R` packages ecosystem.** 

## Package philosophy

The aforementioned objectives are accomplished in `sprawl` by: 

1. Providing simple **wrappers to common-use functions** for reading/writing spatial data (e.g., `readvec` and `writevec` to read/write vector files from/to disk); 
2. Providing **optimized functions for performing some common-use processing tasks**, often exploiting functions provided by less-known packages (e.g., `maskraster`); 
3. Providing custom functions for performing more complex processing tasks (e.g., `extract_rast`) involving the use of different functions and/or packages;
4. Optimizing code execution speed by providing under-the-hood support for multi-core processing using for example `foreach` looping and `raster::MakeCluster` functionality;
4. Simplifying access/further analysis of results, by carefully formatting processing outputs to easy to understand and use `R` objects.

Given this, `sprawl` is expected to be a broadly-aimed (and therefore rather "amorphous") and rapidly-changing package, which functionalities are expected to 1. gradually grow to include additional functions/wrappers, and 2. be sometimes removed/changed as soon as similar or better functionalities start to be provided by different/more focused packages. 

`sprawl` is currently developed and maintained by personnel of the Milan section of CNR-IREA (Institute on Remote Sensing of Environment - National Research Council, Italy - http://www.irea.cnr.it/en/)

## **WORK IN PROGRESS !**

If you stumble on this page, please be advised that **`sprawl` is currently in an early stage 
of development. This means that things are going to change rapidly, and we do not guarantee 
that everything works as expected**. Additionally, be warned that until a first official version 
is released, **functions may change behaviour or even completely disappear while we test different 
approaches and solutions** ! (besides this: we would be happy to have beta-testers !)

## Installation

You can install sprawl from git-hub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("lbusett/sprawl")
```

<font size="2"> _Note that, given its rather broad scope, `sprawl` **imports functions from
several other packages**. Since some of those have quite specific System Requirements, it's 
possible that you'll struggle a bit in installation due to unresolved dependencies. In that 
case, please have a look at the installation error messages to see which package has problems 
in installation and try to install it beforehand (consulting its specific CRAN pages or doing 
a stackoverflow search may help !)._ </font>

## Package Documentation

The main functions available in `sprawl` will bedocumented in `sprawl` website at 
[here](https://lbusett.github.io/sprawl), along with usage examples and benchmarking results. 

## Contributing

We are open for contributions/help in improving `sprawl` and extend its functionalities. 
If you have a **suggestion for and additional functionality** please report it in our [issues](https://github.com/lbusett/sprawl/issues) page. 
If you **wish to contribute to `sprawl` development**, please see our [Contributing page] 
on Git Hub (COMING SOON !).

## Authors

`sprawl` is currently developed and maintained by Lorenzo Busetto and Luigi Ranghetti of 
CNR-IREA (Institute on Remote Sensing of Environment - National Research Council, Italy - 
http://www.irea.cnr.it/en/)

## Citation

To cite package `sprawl` in publications use:

  Lorenzo Busetto and Luigi Ranghetti (2017). sprawl: Spatial Processing (in) R: Advanced
  Workflow Library. R package version 0.1.0.9000.

Please note that this project is released with a [Contributor Code of Conduct](https://lbusett.github.io/sprawl/articles/conduct.html). By participating in this
project you agree to abide by its terms.
