---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tibble.width = Inf)
```

## Extracting statistics for features of a vector file form a multi-band raster file

### Case Study 

You have a raster multi-band file containing the values of an index (e.g., EVI) for multiple
dates, and a vector file with areas from which you wish to either: 
  
  1. Extract the time serie for each pixel contained in polygon ;
  2. Compute summary statistics on the values of the pixels of each polygon, for each date/band
    of the raster

### Solution

You can use `sprawl::extract_rast` to quickly extract both the single-pixel time series, and the 
statistics for each polygon and date

### Example

First of all, open the input raster containing the time series,  and of the 
input vector file containing the polygons (i.e., the ROIs) for which you want the values. 

```{r extract_rast, echo=TRUE, message=FALSE, warning=FALSE}
# Here I'm using test datasets accessed on the filesystem, but on common usage it would as 
# simple as `in_polys <- read_shape("D:/mypath/myfolder/lc_polys.shp"")

library(raster)
library(sprawl)


in_polys <- read_shape(system.file("extdata","lc_polys.shp", package = "sprawl.data"))
in_rast  <- stack(system.file("extdata", "sprawl_EVItest.tif", package = "sprawl.data"))

```

Now, in `in_polys` we have a vector with 13 polygons: 

```{r, echo=FALSE}
in_polys
```

, and in `in_rast` a raster time series with 46 bands:

```{r, echo=FALSE}
in_rast
```

Let's have a look at some bands: 

```{r}
plot_rast(in_rast[[2:7]], limits = c(0,7000), in_poly = in_polys)
```


To extract the values of pixels included in each polygon, you can then use simply: 

```
extracted_values <- extract_rast(in_rast, in_polys)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
extracted_values <- extract_rast(in_rast, in_polys, id_field = "lc_type")
```
`extracted values` is a list containing two components:

- `extracted_values$alldata` contains the values for each extracted pixel, along with information extracted from the vector file. Additionally, the number of pixels extracted from each polygon is shown in the `N_PIX` column, and an identifier to each pixel in the `N` column 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
extracted_values$alldata
```

-  `extracted_values$statdata` contains instead the statistics for each polygon and band. By default, average, standard deviation, minimum, maximum and median are computed (see the help of the function) 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
extracted_values$stats
```

These results can be easily used for performing further analysis or plotting (**coming soon !**)
